---
title: "Presentation Fake"
#subtitle: "⚔<br/>with xaringan"
author: "Anduena Rexhepi"
institute: "University of Ulm"
date: "2021/07/12"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan
## this is how you pronounce the package name
### /ʃaː.'riŋ.ɡan/

---
Slide 1
========================================================

Here you can see a plot without displaying the code that created the plot. 
It's the usual cars plot again...

```{r, echo=FALSE, fig.width =7}
plot(cars)
```
---

Slide 2
========================================================

```{r}
summary(cars)
```
--
```{r}
summary(cars)[1,1]
```
--
```{r}
summary(cars)[2,1]
```

---
Slide 3
========================================================

Now let's talk a little bit about flowers 
```{r, echo=FALSE}
plot(iris)
```
---
Slide 4
========================================================
This is just a random tibble :)

```{r, echo=FALSE, message = FALSE, warning=FALSE}
library(tibble)
library(tidyverse)
library(dplyr)
library(kableExtra)

knitr::kable(tibble(x = 1:4, y = 1, z = x ^ 2 + y)) %>%
   row_spec(1, background = "yellow") %>%
   row_spec(3, background = "yellow")
```

---
End
========================================================
Thank you for your attention!
